A Meta-analysis of Fungicide Spray Schedules to Minimise Yield Loss From Powdery Mildew in Australian Mungbean

### 2020-08-04 paper/paper.Rmd
Remove "Head" from merge conflicts

```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
if (!require("pacman"))
  install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, here, english, pander)

@@

```{r Figure2, echo=FALSE, fig.cap="Season plot"}
SeasonPlot
```

>>>>

```{r MEsummary_Libraries1, message=FALSE, echo=FALSE, include=FALSE}
if (!require("pacman"))
  install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, here, english, pander, lubridate)

@@

```{r Figure2, echo=FALSE, caption="Season plot"}
# Create the data frame for the plot
season_dates <- PM_MB_means %>%
   group_by(trial_ref) %>%
   summarise(
      Planting_date = unique(planting_date),
      Harvest_date = unique(harvest_date),
      First_sign_PM = unique(first_sign_disease),
      season_length = as.Date(unique(harvest_date)) - as.Date(unique(planting_date)),
      cropping_season = "Actual"
   )
mean(ymd(PM_Mdat$planting_date), na.rm = TRUE)

PM_Mdat %>%
  distinct(trial_ref, planting_date, harvest_date,first_sign_disease) %>%
  mutate(planting_date = ymd(planting_date))%>%
  mutate(harvest_date = ymd(harvest_date))%>%
    mutate(cropping_season = case_when(
    is.na(planting_date) | is.na(harvest_date ) ~ "Estimated",
    TRUE ~ "Actual"))%>%
  mutate(season_length = case_when(
    is.na(planting_date) ~ harvest_date - mean(planting_date,na.rm = TRUE),
    is.na(harvest_date) ~ mean(harvest_date,na.rm = TRUE) - planting_date,
    TRUE ~ harvest_date - planting_date
  ))

# For some trials where planting date and Harvest date is missing let's estimate 
#     the season length by using the mean of all season lengths
season_dates[is.na(season_dates$season_length),"cropping_season"] <- "Estimated"

season_dates[is.na(season_dates$Planting_date),"Planting_date"] <- 
   season_dates[is.na(season_dates$Planting_date),"Harvest_date"] - 
   as.numeric(mean(season_dates$season_length, na.rm = TRUE))

season_dates[is.na(season_dates$Harvest_date),"Harvest_date"] <- 
   season_dates[is.na(season_dates$Harvest_date),"Planting_date"] + 
   as.numeric(mean(season_dates$season_length, na.rm = TRUE))

season_dates[is.na(season_dates$season_length),"season_length"] <- 
   mean(season_dates$season_length, na.rm = TRUE)

season_dates$Planting_day <- yday(season_dates$Planting_date)
season_dates$Disease_day <- yday(season_dates$First_sign_PM)

season_dates[c(1:2,6), "Planting_day"] <- 1

season_dates$Harvest_day <-
   season_dates$Planting_day + season_dates$season_length

first_day_month <- c(0, 31, 60, 91, 121, 152, 182, 212, 244, 274) + 1
axis_labels_date <-
   c(
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[1], "%b-%d"),
      # Jan
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[2], "%b-%d"),
      # Feb
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[3], "%b-%d"),
      # March
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[4], "%b-%d"),
      # April
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[5], "%b-%d"),
      # May
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[6], "%b-%d"),
      # June
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[7], "%b-%d"),
      # July
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[8], "%b-%d"),
      # August
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[9], "%b-%d"),
      # Sept
      format(Sys.Date() - yday(Sys.Date()) + first_day_month[10], "%b-%d") # October
   )

# reorder the factors so they will appear in chronological order
# I used First sign because all trials have recorded this
season_dates$trial_ref <-
   factor(season_dates$trial_ref,
          levels = levels(season_dates$trial_ref)[rev(order(season_dates$First_sign_PM))])

# Plot
season_dates %>%
   ggplot() +
   geom_pointrange(aes(
      x = trial_ref,
      y = Disease_day,
      ymin = Planting_day,
      ymax = Harvest_day,
      colour = cropping_season
   )) +
   scale_y_continuous(limits = c(
      0,
      max(
         season_dates$Planting_day +
            season_dates$season_length,
         na.rm = TRUE
      )
   ),
   labels = axis_labels_date,
   breaks = first_day_month) +
   geom_point(aes(x = trial_ref, y = Disease_day)) +
   coord_flip() +
   scale_color_manual(values=c("black","grey70"))+
   ggtitle("Season length and when powdery mildew was first spotted\nin each respective trial")

```
